Multi-Domain Adaptation in Neural Machine Translation with Dynamic Sampling Strategies

### 2021-08-02 2021/wmt/auto_cl_mdmt.tex
WMT submission

\begin{document}
\maketitle
\setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{2pt}
\begin{abstract}
  Building effective Neural Machine Translation models often implies accommodating diverse sets of heterogeneous data so as to optimize performance for the domain(s) of interest. Such multi-source / multi-domain adaptation problems are typically approached through instance selection or reweighting strategies, based on a static assessment of the relevance of training instances with respect to the task at hand. In this paper, we study dynamic data selection strategies that are able to automatically re-evaluate the usefulness of data samples and to evolve a data selection policy in the course of training. Based on the results of multiple experiments, we show that such methods constitute a generic framework to automatically and effectively cater to a variety of real-world situations, from supervised multi-source domain adaptation to multi-domain learning and unsupervised domain adaptation. 
\end{abstract}

@@

It is usual in MT to opportunistically collect training samples from several domains, which means that training instances are distributed according to a mixture $\mathcal{D}^s$ such that $\mathcal{D}^s(x) = \sum_{d=1}^{n_d} \lambda^{s}(d) \mathcal{D}_d(x)$, with $\{\lambda^{s}(d), d=1 \dots n_d\}$ the mixture weights satisfying $\sum_d \lambda^{s}(d)=1$.

The main challenge is then to make the best of this heterogeneous data, with the aim to achieve the optimal performance for the intended test conditions. These might correspond to data from just one of the training domains, as in standard supervised (multi-source) domain adaptation; a more difficult case is when the test data is from one domain unseen in training (unsupervised domain adaptation); in multi-domain adaptation finally, the test distribution is itself a mixture of domains, some of which may also be observed in training.  Without loss of generality, one may then assume that the test distribution takes the form $\mathcal{D}^{t}(x) = \sum_d \lambda^{t}(d) \mathcal{D}_d(x)$ - with only one non-null  component in the case of pure domain adaptation. These settings are illustrated on Figure~\ref{fig:mdmt-lambdas}.
\begin{figure}[h]
  \centering
  \includegraphics[width=0.48\textwidth]{mdmt-lambdas}
  \caption{Training and testing with distribution mismatch. We consider just three domains, and represent vectors of mixture weights $\vlambda^{s}$ and $\vlambda^{t}$ in the 3-dimensional simplex. Training with weights in (a) and testing with weights in (c) is supervised multi-source domain adaptation to domain~2 ($d_2$), while (b)-(c) is the unsupervised version, with no training data from $d_2$; training with weights in (a) and testing with weights in (d) is multi-domain learning, also illustrated with configurations (a)-(e) (training domain $d_1$ is not seen in test), and (b)-(d)  (test domain $d_2$ is unseen in training).}\label{fig:mdmt-lambdas}
\end{figure}

@@

\section{Multi-Domain Automated Curriculum } \label{sec:mdac}
\subsection{Basic principles}
Assuming training data in each of the $n_d$ domains $d_1 \dots d_{n_d}$, we denote the size of the training corpus from domain $d$ as $N^{s}_d$, and $N^{s} = \sum_d N^{s}_d$ is the total number of training samples. We use $\widehat{\mathcal{D}^l_d}$ and $\widehat{\mathcal{D}^t _d}$ to denote the empirical train and test distributions for domain $d$, and $\widehat{\mathcal{D}^{u}}(x;\lambda^{u}) = \sum_{d} \lambda^{u}(d) \widehat{\mathcal{D}^{u}_d}(x)$ for $u\in\{l,t\}$. In our setting,  $\vlambda^t$, and hence $\widehat{\mathcal{D}^t}(x;\vlambda^t)$ are fixed and predefined, approximated with an equivalent number of development corpora.

% Our method
MDAC constructs an adaptative training distribution $\lambda^{l}$ that optimizes the data selection policy along with the training of the NMT model. We parameterize $\lambda^{l}$ by a differentiable function $\lambda^l(\psi)$. We divide the training into many short sessions; in each session $t$, the model is trained with a static data distribution $\lambda^{l}(\psi_t)$. After one learning session, we update the data distribution using the REINFORCE algorithm of \citet{Williams92simple}. The evolution of $\psi$ is thus defined by:
\begin{align*}
\psi_{t+1} &= \psi_t + \mathbf{lr}_{1} * \displaystyle{\mathop{\sum}_{d=1}^{n_d}} R(d) * \frac{\partial \lambda^l(d;\psi_t)}{\partial \psi}, \\
\end{align*}
\begingroup
\allowdisplaybreaks
where reward $R(d)$ is computed as:
\begin{align*}
  R(d) = J^t(\theta_{t+k},\vlambda^t) - J^t(\theta_t,\vlambda^t),
\end{align*}
and where we also define:
\begin{equation}
\begin{array}{rcl}
\theta_{t+i} &=& Update\big(\theta_{t+i-1},[x^i_j,y^i_j]_{j=1}^N\big) \\ \nonumber
x^i_j, y^i_j &\sim& \widehat{D^l_d}(x) \\
J^t(\theta,\lambda_t) &=& \displaystyle{\mathop{\sum}_{d=1}^{n_d}}\lambda^t(d)\displaystyle{\mathop{\sum}_{x^t_d,y^t_d \in \widehat{D^t_d}}} l(\theta,x^t_d,y^t_d).
\end{array}
\end{equation}
\endgroup
% \theta_{t+i-1} - \mathbf{lr_2} \frac{1}{N}\displaystyle{\mathop{\sum}_{j=1}^N}\frac{\partial l(\theta_{t+i-1}, x^i_j,y^i_j)}{\partial \theta}
In these equations, $N$ denotes the size of a batch; $\mathbf{lr}_{1}$ is the learning rate of the sampling distribution; $l(\theta,x,y)$ is the loss of the NMT model on sample $(x,y)$; $J^t(\theta,\lambda_t)$ is the weighted loss aggregated over $n_d$ dev-sets corresponding to the $n_d$ domains.

@@

The work of \citet{Wang20balancing} is also related: it is based on the Bi-level Optimization framework, which aims to find an optimal static distribution $\lambda^{l}$ that will result in the best NMT model with respect to a given target dev set at the end of training. These authors also derive a similar form of update for $\psi$. However, their reward is the cosine similarity between the gradient computed with the training data from one domain and the gradient computed with the dev set. We compare this approach with ours in the experiment section.

@@

\begin{itemize}
\itemsep0em 
\item Generic models trained with predefined mixtures of the training data taking the form:
\begin{align} \label{mixture:trn}
\lambda_{\alpha}(d) = \frac{q_d^{\alpha}}{\displaystyle{\mathop{\sum}_{d=1}^{n_d}q_d^{\alpha}}} &&
q_d = \frac{\mid N^{s}_d \mid}{\displaystyle{N^{s}}} % \mathop{\sum}_{i=1}^K\mid D_i \mid}}
\end{align}
%\setlength{\abovedisplayskip}{2pt}
% \setlength{\belowdisplayskip}{2pt} 
with $\alpha \in \{0,0.25,0.5,0.75,1.0\}$. We denote these as \system{Mixed-$\alpha$} below. \system{Mixed-$0$} uses a uniform distribution, \system{Mixed-$1.0$} the empirical domain distribution.
\item fine-tuned models \citep{Luong15stanford,Freitag16fast}, based on the \system{Mixed-$1.0$} system, further trained on each domain for at most 50~000 iterations, with early stopping when the dev BLEU stops increasing for 5 successive iterations.\fyDone{for ?? iterations} The full fine-tuning (\system{FT-Full}) procedure may update all the parameters of the initial generic model, resulting in six systems, each adapted for one domain, with no parameter sharing across domains.
\item systems trained with fixed data mixtures corresponding to $\lambda^l \in \big[ \lambda_0, \lambda_{0.25}, \lambda_{0.5}, \lambda_{0.75}, \lambda_{1.0}\big]$; these are used in the multi-domain experiments of Section~\ref{ssec:mda};
\item  our own implementations of recent dynamic sampling proposals from the literature: Curriculum Learning (CL) of \citet{Zhang19curriculum} and Differential Data Selection (DDS) of \citet{Wang20balancing} (see details below);
\end{itemize}

@@

@@

In a fourth experiment (\emph{few-shot adaptation}), given training data in 6 domains and a small development set of a new domain (\domain{News} in our case), we aim to build an NMT model which performs well for the unseen domain.

@@

We now turn to a more realistic scenario and consider multi-domain adaptation, which aims to train one single system with optimal performance averaged over 6 domains. This setting targets a uniform test distribution $\lambda^t = \lambda_0$. In this situation, CL \citep{Zhang19curriculum} does not apply. We therefore only contrast the performance of MDAC, DDS and several fixed training data distribution $\vlambda^l \in \big[ \vlambda_0, \vlambda_{0.25}, \vlambda_{0.5}, \vlambda_{0.75}, \vlambda_{1.0}\big]$, where $\vlambda_{\alpha}$ is defined according to equation~\eqref{mixture:trn}.

We again initialize MDAC and DDS with two distribution $\lambda_0$ and $\lambda_1$. According to Table~\ref{tab:multi-da}, MDAC achieves the best performance with initial (uniform) $\lambda_0$. The same conclusion holds for DDS. For this configuration, MDAC outperforms static training distributions including $\big[ \lambda_0, \lambda_{0.75}, \lambda_{1.0}\big]$ by a significant margin, and performs slightly better than $\big[ \lambda_{0.25}, \lambda_{0.5} \big]$. This indicates that MDAC allows us to skip the somewhat heuristic choice of the optimal training mixture.

@@

\begin{table*}[htbp]
  \centering \small
  \begin{tabular}{|l|*{10}{r|}} \cline{1-2} \cline{4-11}
    domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{news}}& \hfill &domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{mean}  \\ 
\cline{1-2} \cline{4-11}
    \multicolumn{2}{|c|}{\sl Unseen domain} & &\multicolumn{8}{c|}{\sl Training with 30 clusters} \\ 
\cline{1-2} \cline{4-11}
    \system{Mixed-0}      & 25.7 & &\system{DDS($\vlambda^*, \vlambda_d$)}&38.3&60.1&50.3&35.8&49.1&90.1&53.9\\
    \system{Mixed-0.25} & 25.8 & &\system{MDAC($\vlambda^*, \vlambda_d$)}&39.2$^*$&61.6$^*$&52.0$^*$&38.2$^*$&49.1&89.7&55.0$^*$\\ \cline{4-11}
    \system{Mixed-0.5}   &26.5\\
    \system{Mixed-0.75} &26.8\\
    \system{Mixed-1} &26.9 \\
    \cline{1-2}
     \system{DDS($\vlambda_0, \vlambda_{news}$)} &26.3 \\
     \system{MDAC($\vlambda_0, \vlambda_{news}$)} &26.3 \\
     \cline{1-2}
  \end{tabular}
  \caption{Few-shot adaptation (left) and unsupervised adaptation (right). For a given line, each column corresponds to one distinct system. ($^*$) MDAC is significantly better than DDS.}
  \label{tab:unsupervised-da}
\end{table*}

\subsection{Unseen domain}\label{ssec:uda}
The left part of Table~\ref{tab:unsupervised-da} displays the performance on the unseen domain \domain{news} for NMT systems trained with the mixtures $\lambda^l \in \big[ \lambda_0, \lambda_{0.25}, \lambda_{0.5}, \lambda_{0.75}, \lambda_{1.0}\big]$ and with dynamic data selection (MDAC and DDS). These systems have insignificant differences in BLEU, showing that dynamic mixture does not improve the robustness of the NMT system against unseen domains. However, the fact that the performance of MDAC and DDS is close to the best performance is a sign that they can also apply in such challenging situations. % the robustness of the NMT model.

@@

\section{Conclusion and outlook \label{sec:conclusion}}
\fyDone{Write conclusion}
In this study, we have presented a generic framework to perform a variety of standard adaptation tasks for machine translation, ranging from the conventional supervised domain adaptation to multi-domain adaptation and few-shot DA. By experimenting with all these settings, we have shown that the same algorithm, aimed at automatically finding an effective data sampling scheme during the course of training, could be used in all these situations. This algorithm, we believe, provides us with a more sound approach to (multi-domain) DA than existing heuristics and dispenses with the costly search of optimal meta-parameters. Another contribution of our work is an experimental comparison of recent approaches to dynamic data selection.

>>>>

\begin{document}
\maketitle
\setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{2pt}
\begin{abstract}
  Building effective Neural Machine Translation models often implies accommodating diverse sets of heterogeneous data so as to optimize performance for the domain(s) of interest. Such multi-source / multi-domain adaptation problems are typically approached through instance selection or reweighting strategies, based on a static assessment of the relevance of training instances with respect to the task at hand. In this paper, we study dynamic data selection strategies that are able to automatically re-evaluate the usefulness of data samples and to evolve a data selection policy in the course of training. Based on the results of multiple experiments, we show that such methods constitute a generic framework to automatically and effectively cater to a variety of real-world situations, from multi-source domain adaptation to multi-domain learning and unsupervised domain adaptation. 
\end{abstract}

@@

It is usual in MT to opportunistically collect training samples from several domains, which means that training instances are distributed according to a mixture $\mathcal{D}^s$ such that $\mathcal{D}^s(x) = \sum_{d=1}^{n_d} \lambda^{s}(d) \mathcal{D}_d(x)$, with $\{\lambda^{s}(d), d=1 \dots n_d\}$ the mixture weights satisfying $\sum_d \lambda^{s}(d)=1$. To clarify the ambiguity in the notation of $\lambda$ and $\vlambda$, regardless the superscripts and the subscripts, $\lambda$ is used to denote a scalar and $\vlambda$ is used to denote a vector, for example, $\lambda^{t}(d)$ is the $d^{th}$ element of the vector $\vlambda^{t}$, which represents the probability distribution over the set of domains.

The main challenge is then to make the best of this heterogeneous data, with the aim to achieve the optimal performance for the intended test conditions. These might correspond to data from just one of the training domains, as in standard supervised (multi-source) domain adaptation; a more difficult case is when the test data is from one domain unseen in training (unseen domain adaptation); in multi-domain adaptation finally, the test distribution is itself a mixture of domains, some of which may also be observed in training.  Without loss of generality, one may then assume that the test distribution takes the form $\mathcal{D}^{t}(x) = \sum_d \lambda^{t}(d) \mathcal{D}_d(x)$ - with only one non-null  component in the case of pure domain adaptation. These settings are illustrated on Figure~\ref{fig:mdmt-lambdas}.
\begin{figure}[h]
  \centering
  \includegraphics[width=0.48\textwidth]{mdmt-lambdas}
  \caption{Training and testing with distribution mismatch. We consider just three domains, and represent vectors of mixture weights $\vlambda^{s}$ and $\vlambda^{t}$ in the 3-dimensional simplex. Training with weights in (a) and testing with weights in (c) is supervised multi-source domain adaptation to domain~2 ($d_2$), while (b)-(c) is the unsupervised version, with no training data from $d_2$; training with weights in (a) and testing with weights in (d) is multi-domain learning, also illustrated with configurations (a)-(e) (training domain $d_1$ is not seen in test), and (b)-(d)  (test domain $d_2$ is unseen in training).}\label{fig:mdmt-lambdas}
\end{figure}

@@

\section{Multi-Domain Automated Curriculum } \label{sec:mdac}
\subsection{Basic principles}
Assuming training data in each of the $n_d$ domains $d_1 \dots d_{n_d}$, we denote the size of the training corpus from domain $d$ as $N^{s}_d$, and $N^{s} = \sum_d N^{s}_d$ is the total number of training samples. We use $\widehat{\mathcal{D}^l_d}$ and $\widehat{\mathcal{D}^t_d}$ to denote the empirical train and test distributions for domain $d$, and $\widehat{\mathcal{D}^{u}}(x;\vlambda^{u}) = \sum_{d} \lambda^{u}(d) \widehat{\mathcal{D}^{u}_d}(x)$ for $u\in\{l,t\}$. In our setting,  $\vlambda^t$, and hence $\widehat{\mathcal{D}^t}(x;\vlambda^t)$ are fixed and predefined, approximated with an equivalent number of development corpora.

% Our method
MDAC constructs an adaptative training distribution $\vlambda^{l}$ that optimizes the data selection policy along with the training of the NMT model. We parameterize $\vlambda^{l}$ by a differentiable function $\vlambda^l(\psi)$, which will be described in detail in Section \ref{ssec:dds-sys}. We divide the training into many short sessions; in each session $t$, the model is trained with a static data distribution $\vlambda^{l}(\psi_t)$. After one learning session, we update the data distribution using the REINFORCE algorithm of \citet{Williams92simple}. The evolution of $\psi$ is thus defined by:
\begin{align*}
\psi_{t+1} &= \psi_t + \mathbf{lr}_{1} * \displaystyle{\mathop{\sum}_{d=1}^{n_d}} R(d) * \frac{\partial \lambda^l(d;\psi_t)}{\partial \psi}, \\
\end{align*}
\begingroup
\allowdisplaybreaks
where reward $R(d)$ is computed as:
\begin{align*}
  R(d) = J^t(\theta_{t+k},\vlambda^t) - J^t(\theta_t,\vlambda^t),
\end{align*}
and where we also define:
\begin{equation}
\begin{array}{rcl}
\theta_{t+i} &=& Update\big(\theta_{t+i-1},[x^i_j,y^i_j]_{j=1}^N\big) \\ \nonumber
x^i_j, y^i_j &\sim& \widehat{D^l_d}(x) \\
J^t(\theta,\vlambda^t) &=& \displaystyle{\mathop{\sum}_{d=1}^{n_d}}\lambda^t(d)\displaystyle{\mathop{\sum}_{x^t_d,y^t_d \in \widehat{D^t_d}}} l(\theta,x^t_d,y^t_d).
\end{array}
\end{equation}
\endgroup
% \theta_{t+i-1} - \mathbf{lr_2} \frac{1}{N}\displaystyle{\mathop{\sum}_{j=1}^N}\frac{\partial l(\theta_{t+i-1}, x^i_j,y^i_j)}{\partial \theta}
In these equations, $N$ denotes the size of a batch; $\mathbf{lr}_{1}$ is the learning rate of the sampling distribution; $l(\theta,x,y)$ is the loss of the NMT model on sample $(x,y)$; $J^t(\theta,\vlambda^t)$ is the weighted loss aggregated over $n_d$ dev-sets corresponding to the $n_d$ domains.

@@

The work of \citet{Wang20balancing} is also related: it is based on the Bi-level Optimization framework, which aims to find an optimal static distribution $\vlambda^{l}$ that will result in the best NMT model with respect to a given target dev set at the end of training. These authors also derive a similar form of update for $\psi$. However, their reward is the cosine similarity between the gradient computed with the training data from one domain and the gradient computed with the dev set. We compare this approach with ours in the experiment section.

@@

\begin{itemize}
\itemsep0em 
\item Generic models trained with predefined mixtures of the training data taking the form:
\begin{align} \label{mixture:trn}
\lambda_{\alpha}(d) = \frac{q_d^{\alpha}}{\displaystyle{\mathop{\sum}_{d=1}^{n_d}q_d^{\alpha}}} &&
q_d = \frac{\mid N^{s}_d \mid}{\displaystyle{N^{s}}} % \mathop{\sum}_{i=1}^K\mid D_i \mid}}
\end{align}
%\setlength{\abovedisplayskip}{2pt}
% \setlength{\belowdisplayskip}{2pt} 
with $\alpha \in \{0,0.25,0.5,0.75,1.0\}$. We denote these as \system{Mixed-$\alpha$} below. \system{Mixed-$0$} uses a uniform distribution, \system{Mixed-$1.0$} the empirical domain distribution.
\item fine-tuned models \citep{Luong15stanford,Freitag16fast}, based on the \system{Mixed-$1.0$} system, further trained on each domain for at most 50~000 iterations, with early stopping when the dev BLEU stops increasing for 5 successive iterations.\fyDone{for ?? iterations} The full fine-tuning (\system{FT-Full}) procedure may update all the parameters of the initial generic model, resulting in six systems, each adapted for one domain, with no parameter sharing across domains.
\item systems trained with fixed data mixtures corresponding to $\vlambda^l \in \big[ \vlambda_0, \vlambda_{0.25}, \vlambda_{0.5}, \vlambda_{0.75}, \vlambda_{1.0}\big]$; these are used in the multi-domain experiments of Section~\ref{ssec:mda};
\item  our own implementations of recent dynamic sampling proposals from the literature: Curriculum Learning (CL) of \citet{Zhang19curriculum} and Differential Data Selection (DDS) of \citet{Wang20balancing} (see details below);
\end{itemize}

@@

The computational cost of our approach is due to the simulation step, which is conducted after every 2000 iterations to compute the reward of each domain. During the simulation step, we update the temporary checkpoint with $k$ updates for each domain, which cost as much as $k$ training updates. Therefore, we execute $k \times n_d$ updates in total after every 2000 iterations. Our algorithm approximately costs $1 + \frac{k \times n_d}{2000}$ times as much as a standard training.

@@

In a fourth experiment (\emph{unsupervised domain adaptation}), given training data in 6 domains and a small development set of a new domain (\domain{News} in our case), we aim to build an NMT model which performs well for the unseen domain.

@@

We now turn to a more realistic scenario and consider multi-domain adaptation, which aims to train one single system with optimal performance averaged over 6 domains. This setting targets a uniform test distribution $\vlambda^t = \vlambda_0$. In this situation, CL \citep{Zhang19curriculum} does not apply. We therefore only contrast the performance of MDAC, DDS and several fixed training data distribution $\vlambda^l \in \big[ \vlambda_0, \vlambda_{0.25}, \vlambda_{0.5}, \vlambda_{0.75}, \vlambda_{1.0}\big]$, where $\vlambda_{\alpha}$ is defined according to equation~\eqref{mixture:trn}.

We again initialize MDAC and DDS with two distribution $\vlambda_0$ and $\vlambda_1$. According to Table~\ref{tab:multi-da}, MDAC achieves the best performance with initial (uniform) $\vlambda_0$. The same conclusion holds for DDS. For this configuration, MDAC outperforms static training distributions including $\big[ \vlambda_0, \vlambda_{0.75}, \vlambda_{1.0}\big]$ by a significant margin, and performs slightly better than $\big[ \vlambda_{0.25}, \vlambda_{0.5} \big]$. This indicates that MDAC allows us to skip the somewhat heuristic choice of the optimal training mixture.

@@

\begin{table*}[htbp]
  \centering \small
  \begin{tabular}{|l|*{10}{r|}} \cline{1-2} \cline{4-11}
    domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{news}}& \hfill &domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{mean}  \\ 
\cline{1-2} \cline{4-11}
    \multicolumn{2}{|c|}{\sl Unseen domain} & &\multicolumn{8}{c|}{\sl Training with 30 clusters} \\ 
\cline{1-2} \cline{4-11}
    \system{Mixed-0}      & 25.7 & &\system{DDS($\vlambda^*, \vlambda_d$)}&38.3&60.1&50.3&35.8&49.1&90.1&53.9\\
    \system{Mixed-0.25} & 25.8 & &\system{MDAC($\vlambda^*, \vlambda_d$)}&39.2$^*$&61.6$^*$&52.0$^*$&38.2$^*$&49.1&89.7&55.0$^*$\\ \cline{4-11}
    \system{Mixed-0.5}   &26.5\\
    \system{Mixed-0.75} &26.8\\
    \system{Mixed-1} &26.9 \\
    \cline{1-2}
     \system{DDS($\vlambda_0, \vlambda_{news}$)} &26.3 \\
     \system{MDAC($\vlambda_0, \vlambda_{news}$)} &26.3 \\
     \cline{1-2}
  \end{tabular}
  \caption{Unseen domain adaptation (left) and automatic clustering adaptation (right). For a given line, each column corresponds to one distinct system. ($^*$) MDAC is significantly better than DDS.}
  \label{tab:unsupervised-da}
\end{table*}

\subsection{Unseen domain}\label{ssec:uda}
The left part of Table~\ref{tab:unsupervised-da} displays the performance on the unseen domain \domain{news} for NMT systems trained with the mixtures $\vlambda^l \in \big[ \vlambda_0, \vlambda_{0.25}, \vlambda_{0.5}, \vlambda_{0.75}, \vlambda_{1.0}\big]$ and with dynamic data selection (MDAC and DDS). These systems have insignificant differences in BLEU, showing that dynamic mixture does not improve the robustness of the NMT system against unseen domains. However, the fact that the performance of MDAC and DDS is close to the best performance is a sign that they can also apply in such challenging situations. % the robustness of the NMT model.

@@

\section{Conclusion and outlook \label{sec:conclusion}}
\fyDone{Write conclusion}
In this study, we have presented a generic framework to perform a variety of standard adaptation tasks for machine translation, ranging from the conventional supervised domain adaptation to multi-domain adaptation and unseen domain adaptation. By experimenting with all these settings, we have shown that the same algorithm, aimed at automatically finding an effective data sampling scheme during the course of training, could be used in all these situations. This algorithm, we believe, provides us with a more sound approach to (multi-domain) DA than existing heuristics and dispenses with the costly search of optimal meta-parameters. Another contribution of our work is an experimental comparison of recent approaches to dynamic data selection.
